\section{Experiments}
We focus the main paper on the smallest set of settings needed to establish the scientific case.

\paragraph{Datasets and held-out metrics.}
Camelyon17 is the primary persistent anchor under hospital shift, evaluated with held-out hospital-2 loss, accuracy, calibration, and the teacher-tail stress diagnostic.
CelebA is the transient subgroup-shift contrast, CivilComments is the clearest non-vision selector-verdict reversal under overall loss and official WILDS worst-group loss, and ACSIncome is the geographic-shift regression extension with held-out MSE and tail MSE.
Because hospital~2 is the held-out deployment domain in Camelyon17, held-out hospital-2 loss is the primary reliability view and coincides with worst-domain loss there.
ACSIncome trains on Census divisions $\{1,2,3,5,7,9\}$, validates on $\{4,8\}$, and tests on $\{6\}$ under geographic shift.

\paragraph{Training families.}
The main paper uses two core training stacks:
ERM on frozen embeddings and end-to-end Camelyon17 finetuning.
CivilComments uses frozen DistilBERT embeddings with linear probes in the main text, while the strongest end-to-end anchor is tested on Camelyon17.
Table~\ref{tab:selector-comparison} keeps the absolute Camelyon17 selector comparison, including the baseline reference row, and adds compact selector-verdict rows for frozen CivilComments and ACSIncome.
Appendix~\ref{app:civilcomments-text-e2e} adds a ten-seed end-to-end CivilComments corroboration on an official-group-aware validation surface, but Camelyon17 remains the cleaner end-to-end anchor.
Supporting adaptive runs are deferred to the appendix because the paper's main claim is selection-level, not optimizer-level.

\paragraph{Main stress-test setting.}
We use soft-clipped P95 as the main suppressive stress-test setting.
Appendix dose-response sweeps show that the selected-checkpoint harm weakens at P97/P99 but does not disappear immediately on the strongest Camelyon anchors.
Higher clip thresholds are retained as supportive appendix sweep detail rather than as co-equal main-text settings.

\paragraph{Selected versus fixed checkpoints.}
Each suite reports two views.
The main view uses the actual proxy-selected checkpoint.
The robustness view compares against a matched fixed horizon: epoch 30 for frozen-embedding ERM and epoch 10 for end-to-end finetuning.
This matters because the CelebA ERM result is transient while the Camelyon17 cases are persistent.

\paragraph{Sample sizes and controls.}
The core ERM, objective-family, and finetuning sweeps use $n=10$ seeds.
The objective-family control section compares soft clipping, GCE $q=0.7$, focal loss \citep{lin2017focalloss}, and label smoothing on the same Camelyon17 ERM stack, with hard-bootstrap, teacher-free held-out loss-tail, checkpoint-averaging, and end-to-end Camelyon17 finetune controls summarized in the appendix.
Additional sweep detail, uncertainty summaries, and supporting adaptive controls are moved to the appendix.
