\section{Reproducibility}
All main reported sweeps use explicit seed sets and artifact-backed CSV summaries stored in the repository.
The command-backed paper-facing tables and figures listed in the supplement are generated from those artifacts by scripts in \texttt{src/scripts}; a small number of supporting sensitivity/audit tables are included as static summaries with their status documented in the supplement.
The submission package includes an anonymized supplement archive; reviewers should find \texttt{supplement/README.md}, \texttt{supplement/SUPPLEMENT\_COMMANDS.md}, and \texttt{supplement/ASSET\_TERMS.md} there.

The main training families use $n=10$ seeds.
Core Camelyon17 ERM runs train a linear head on cached ResNet50 embeddings for 30 epochs with AdamW, learning rate $10^{-3}$, batch size $512$, weight decay $10^{-4}$, and evaluation batch size $2048$.
CelebA ERM uses cached ResNet50 embeddings with a width-256 head, AdamW, learning rate $10^{-3}$, batch size $512$, weight decay $10^{-4}$, 30 epochs, and evaluation batch size $2048$.
Frozen CivilComments uses cached \texttt{distilbert-base-uncased} embeddings with a linear head, AdamW, learning rate $10^{-3}$, batch size $512$, weight decay $10^{-4}$, 30 epochs, and evaluation batch size $2048$.
Camelyon17 finetuning uses a 10-epoch end-to-end recipe with AdamW, learning rate $10^{-4}$, batch size $128$, weight decay $10^{-4}$, evaluation batch size $256$, and \texttt{layer4} unfrozen.
The appendix end-to-end CivilComments support uses \texttt{distilbert-base-uncased} finetuning for 10 epochs with AdamW, learning rate $2\times10^{-5}$, batch size $16$, evaluation batch size $32$, weight decay $0.01$, and gradient clipping at $1.0$.
ACSIncome uses a width-256 two-hidden-layer MLP with Adam, learning rate $10^{-3}$, batch size $2048$, weight decay $10^{-4}$, and 50 epochs.
All reported training and evaluation were run on a single NVIDIA GeForce RTX 5090 workstation with 32607 MiB ($\approx$32 GB) VRAM; the longest saved main-supporting run in the repository is the ten-seed end-to-end CivilComments sweep, whose manifest records roughly 12 GPU-hours total.
Camelyon17 and CivilComments are used through WILDS \citep{koh2021wilds}; the underlying dataset sources include CAMELYON17 \citep{bejnordi2017camelyon}, CelebA \citep{liu2015celeba}, and Folktables/ACSIncome \citep{ding2021folktables}.
The supplement bundle includes the exact commands, minimal dependency list, and saved claim-bearing artifacts needed to regenerate the listed command-backed paper-facing outputs from saved repository artifacts, including the ACSIncome regression extension under \texttt{artifacts/metrics/acs\_income/}. In particular, the bundled regeneration path covers the main selector table, the core-case summary, the Camelyon selector-diagnostic table, the Camelyon17 ERM selector-dose, validation-accuracy selector sensitivity, selector-averaging sensitivity, and leave-one-hospital-out selector-only diagnostics, the hard-bootstrap support table, the GCE $q=0.7$ corroboration table, the teacher-free held-out loss-tail table, the objective-family finetune support table, the persistence-support table, the per-bank robustness tables, the seed-count and paired-interval summaries, and the Camelyon dose-response appendix table from saved CSV artifacts rather than retraining. Static support tables and their provenance status are documented separately in the supplement. Viewed narrowly, the package therefore provides an artifact-backed regeneration path for the listed claim-bearing results and a compact selector-comparison suite for comparing alternative checkpoint selectors on the released runs without retraining. Full end-to-end reruns additionally require the external benchmark assets and the surrounding project environment. \texttt{supplement/ASSET\_TERMS.md} summarizes the credited third-party assets and the verified governing terms used in the submission package.
Camelyon17 is used through the WILDS patch-based release stored locally as \texttt{camelyon17\_v1.0}.
The current WILDS dataset page states that the public release is distributed under CC0, while the CAMELYON17 challenge website contains mixed license notices across its public pages.
We therefore do not redistribute any raw third-party images in the supplement and restrict the artifact package to code and derived summaries.

We intentionally keep the main paper focused on a small set of claim-bearing outputs:
the core-case summary, the selector-comparison table, the divergence figure, the ranking-reversal table, and the main same-stack mechanism exhibit.
